---
title: "FARS Functions Overview"
author: "Tarso Rodriguez"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

*FARS* package is a cluster of functions that can handle information about [Fatality Analysis Reporting System](https://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS)) (FARS) which is provided by US National Highway Traffic Safety Administration through a file. Each file has the information about a specific year.

Below is a list of all functions with its short description.

```{r, echo=FALSE, results='hide'}
source("../R/fars_functions.R")
```

**fars_read**: Loads a specific fars file to a data frame
```{r ReadFile, cache=TRUE}
df_fars_file <- fars_read("../inst/extdata/accident_2013.csv.bz2")
head(df_fars_file)
```

**make_filename**: Builds a string with the name of file that will be loaded based on the year given by the user
```{r CreateFileName, cache=TRUE}
filename <- make_filename(2013)
filename
```

**fars_read_years**: Creates a list of all months in the files
```{r ListMonths, cache=TRUE}
setwd(system.file("extdata", package = "fars"))
list_of_months <- fars_read_years(c(2013, 2014, 2015))
head(list_of_months)
```

**fars_summarize_years**: Summarizes the number of occurrencies in each month by year
```{r OccurrencySummary, cache=TRUE}
setwd(system.file("extdata", package = "fars"))
df_occurrency_summary <- fars_summarize_years(c(2013, 2014, 2015))
head(df_occurrency_summary)
```

**fars_map_state**: Plots a map of a state showing the places of each accident that happend in a specific year
```{r Map, cache=TRUE, fig.align='center', fig.height=4, fig.width=4}
setwd(system.file("extdata", package = "fars"))
fars_map_state(1, 2013)
```
